### 2019-06-06 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
I have some small bugs, but all is good

Under observation model \modeltrois{} no sensing information is available and the previous algorithms cannot be used, as the sum of sensing information $S_k^j(t)$ and thus the empirical mean $\widehat{\mu}_k^j(t)$ cannot be computed, hence neither the indices $g_k^j(t)$. However, one can still define a notion of \emph{empirical reward} received from arm $k$ by player $j$, by introducing
%
% \vspace*{-5pt}
\begin{equation}
  \widetilde{S_k}^j(t) = \sum_{t=1}^T r^j(t) \indic(A^j(t) = k)
  \ \ \ \text{and letting} \ \ \ \widetilde{\mu_k}^j(t) := \widetilde{S_k}^j(t) \;/\; T_k^j(t).
\end{equation}

Note that $\widetilde{\mu_k}^j(t)$ is no longer meant to be an unbiased estimate of $\mu_k$ as it also takes into account the collision information, that is present in the reward. Based on this empirical reward, one can similarly defined modified indices as
%
\begin{equation}\label{eq:5:indexTilde}
  \widetilde{g_k}^j(t) = \begin{cases}
      \widetilde{\mu_k}^j(t)  + \sqrt{  f(t) / (2T_k^j(t))}
      &\text{for } \UCB, \\
      \sup\left\{ q \in [0, 1]: T_k^j(t)\times \kl(\widetilde{\mu_k}^j(t), q) \leq f(t) \right\}
      &\text{for } \klUCB.
  \end{cases}
\end{equation}

Given any of these two index policies (\UCB{} or \klUCB), the \Selfish{} algorithm is defined by,
%
\begin{equation}
  A^j(t) = \argmax_{ k \in [K]} \ \widetilde{g_k}^j(t-1).\label{algo:5:Selfish}
\end{equation}
The name comes from the fact that each player is targeting, in a ``selfish'' way, the arm that has the highest index, instead of accepting to target only one of the $M$ best.
The reason that this may work precisely comes from the fact that $\widetilde{g_k}^j(t)$ is no longer an upper-confidence on $\mu_k$,
but some hybrid index that simultaneously increases when a transmission occurs and decreases when a collision occurs.

This behavior is easier to be understood for the case of \Selfish-\UCB{} in which, letting $N_k^{j,C}(t) = \sum_{s=1}^t \indic(C^j(t))$ be the number of collisions on arm $k$, one can show that the hybrid \Selfish{} index induces a penalty proportional to the fraction of collision on this arm and the quality of the arm itself:
\begin{equation}
  \widetilde{g_k}^j(t) = g_k^j(t) -
  \underbrace{\left(\frac{N_k^{j,C}(t)}{N_k^j(t)}\right)}_{\text{fraction of collisions}}
  \underbrace{\left(\frac{1}{N_k^{j,C}(t)}\sum_{t=1}^{T}Y_{A^j(t),t} \indic(C^j(t)) \indic(A^j(t) = k)\right)}_{\text{estimate of } \mu_k }.
\end{equation}

@@

\paragraph{Index policies.}
%
The approaches we now describe for multi-player bandits can be used in combination with any index policy, but we restrict our presentation to UCB algorithms, for which strong theoretical guarantees can be obtained. In particular, we focus on two types of indices:
\UCB{} indices \citep{Auer02}
and \klUCB{} indices \citep{KLUCBJournal}, that can be defined for each player $j$ in the following way.
%
Letting $S_k^j(t) := \sum_{s=1}^t Y_{k,s} \indic(A^j(t) = k)$ the current sum of rewards obtained by player $j$ for arm $k$,
then $\widehat{\mu}_k^j(t) = S_k^j(t)/T_k^j(t)$ (if $T_k^j(t)\neq 0$) is the empirical mean of arm $k$ for player $j$, and thus one can define the index
\begin{equation}\label{eq:5:indexFor_UCB_klUCB}
  g_k^j(t) := \begin{cases}
      \widehat{\mu}_k^j(t)  + \sqrt{  f(t) / (2T_k^j(t))}
      &\text{for } \UCB, \\
      \sup\left\{ q \in [0, 1]: T_k^j(t)\times \kl(\widehat{\mu}_k^j(t), q) \leq f(t) \right\}
      &\text{for } \klUCB,
  \end{cases}
\end{equation}
where $f(t)$ is some \emph{exploration function}. $f(t)$ is usually taken to be $\log(t)$ in practice, and slightly larger in theory, which ensures that  $\Pr(g_k^j(t) \geq \mu_k) \gtrsim 1 - 1/t$ (see \cite{KLUCBJournal}).
A classical (single-player) UCB algorithm aims at the arm with largest index. However, if each of the $M$ players selects the arm with largest UCB, all the players will end up colliding most of the time on the best arm.
To circumvent this problem, several coordination mechanisms have emerged, that rely on \emph{ordering} the indices and targeting \emph{one of} the $M$-best indices.

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(1) \sim \cU([K])$ and $C^j(1)=\mathrm{False}$ \\
              \For{$t = 0, \dots, T - 1$}{
                  %
                  \eIf{$A^j(t) \notin \TopM(t)$}{
                    \eIf(\tcp*[f]{collision}){$C^j(t)$}{
                      $A^j(t+1) \sim \cU \left(\TopM(t)\right)$
                      \tcp*[f]{randomly switch}
                      }(\tcp*[f]{randomly switch on an arm that had smaller UCB at $t-1$}){
                        $A^j(t+1) \sim \cU \left(\TopM(t) \cap \left\{k : g_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      }
                    }{
                      $A^j(t+1) = A^j(t)$
                      \tcp*[f]{stays on the same arm}
                    }
                  Play arm $A^j(t+1)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \RandTopM{} decentralized learning policy]{The \RandTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:RandTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(1) \sim \cU([K])$ and $C^j(1)=\mathrm{False}$ and $s^j(1)=\mathrm{False}$ \\
              \For{$t = 0, \dots, T-1$}{
                   \uIf(\tcp*[f]{transition $(3)$ or $(5)$}){
                      $A^j(t) \notin \TopM(t)$}
                    {
                      $A^j(t+1) \sim \cU \left(\TopM(t) \cap \left\{k : g_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      \tcp*[f]{not empty} \\
                      % \tcp*[f]{randomly switch on an arm that had smaller UCB at $t-1$}
                      $s^j(t+1) = \mathrm{False}$
                      \tcp*[f]{aim at an arm with a smaller UCB at $t-1$}
                    }
                    \uElseIf(\tcp*[f]{collision and not fixed}){
                        $C^j(t)$ \emph{and} $\overline{s^j(t)}$}
                      {
                        $A^j(t+1) \sim \cU \left(\TopM(t)\right)$
                        \tcp*[f]{transition $(2)$} \\
                        $s^j(t+1) = \mathrm{False}$
                    }
                    \Else(\tcp*[f]{transition $(1)$ or $(4)$}){
                      $A^j(t+1) = A^j(t)$ \tcp*[f]{stay on the previous arm} \\
                      $s^j(t+1) = \mathrm{True}$ \tcp*[f]{become or stay fixed on a ``chair''}
                    }
                  Play arm $A^j(t+1)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \MCTopM{} decentralized learning policy]{The \MCTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:MCTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

\begin{smallproof}
  %
  %     Recall $g_k^j(t) \in \mathbb{R}$ denote the index of arm $k$ for user $j$ at time $t$.
  %     As only user $j$ is considered here, the superscript $j$ is dropped.
  %
  Fix $k\in\Mworst$ and a player $j \in [M]$.
  The key observation is that for \MCTopM, \RandTopM{} as well as the \rhoRand{} algorithm, it holds that
  \begin{equation}\left(A^j(t) = k\right) = \left(A^j(t) = k , \exists m \in \Mbest : g_m^j(t) < g_k^j(t) \right).\label{eq:5:KeyInclusion}\end{equation}
  Indeed, for the three algorithms, an arm selected at time $t+1$ belongs to the set $\TopM(t)$ of arms with $M$ largest indices.
  If the sub-optimal arm $k$ is selected at time $t$, it implies that $k \in \TopM(t)$, and, because there are $M$ arms in both \Mbest{} and $\TopM(t)$, one of the arms in \Mbest{} must be excluded from $\TopM(t)$.
  In particular, the index of arm $k$ must be larger than the index of this particular arm $m$.

  Thanks to \eqref{eq:5:KeyInclusion} and if $\Pr_{\bm{\mu}} $ denote here the probability under model $\bm{\mu}$, it is easy to decompose the number of selections of arm $k$ by user $j$ up to round $T$ as
  \begin{align*}
  \E_{\mu}[T_k^j(T)]
  &= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
  = \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k \right).\\
  %&= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\Mbest,\; g_m(t) < g_k(t) \right) \\
  &= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in[M]:\; U_{m^*}^j(t) < g_k^j(t) \right).
  %
  \end{align*}

@@

  \begin{align}
    \E_{\mu}[T_k^j(T)] &\leq
    \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m_1 \in [M]: \; U_{m_1^*}(t) < \mu_m^* \right) + \notag \\
    \;\;\;\;
    \sum_{t=1}^T\Pr_{\bm{\mu}} & \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; U_{m_2^*}(t) \leq g_k(t) , \forall {m_3} \in [M]: \;  U_{{m_3}^*}(t) \geq \mu_{m_3}^* \right) \notag \\
    &\leq \sum_{m_1=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(U_{m_1^*}(t) < \mu_{m_1}^* \right) + \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; \mu_{m_2}^* \leq g_k(t)\right) \notag \\
    %
    & \leq \sum_{m_1=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( U_{m_1^*}(t) < \mu_{m_1}^* \right)
    + \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq g_k(t) \right)
    \label{eq:5:sumOfProbaForTkj}
  \end{align}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in [M]$.

@@

  \begin{lemma}\label{lem:5:Fact1KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
      For any arm $k$, if $g_k^{j}(t)$ is the \klUCB{} index with exploration function $f(t)=\log(t)+3\log\log(t)$,
      \begin{equation}
        \sum_{t=1}^T \Pr_{\bm{\mu}} \left(g_k^{j}(t) < \mu_k\right) \leq 3 + 4e \log\log(T).
      \end{equation}
  \end{leftbar}  % XXX leftbar lemmabar, comment if needed
  \end{lemma}

@@

  \begin{lemma}\label{lem:5:Fact2KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    For any arms $k$ and $k'$ such that $\mu_{k'} > \mu_{k}$, if $g_k^{j}(t)$ is the kl-UCB index with exploration function $f(t)$,
    \begin{small} % XXX
      \begin{align*}
        &\sum_{t=1}^T\Pr_{\bm{\mu}} \left( A^j(t) = k, \mu_{k'} \leq g_k^{j}(t) \right) & \leq  \frac{f(T)}{\kl(\mu_k,\mu_{k'})}
        + \sqrt{2\pi} \sqrt{\frac{\kl'(\mu_k,\mu_{k'})^2}{\kl(\mu_k,\mu_{k'})^3}}\sqrt{f(T)} + 2\left(\frac{\kl'(\mu_k,\mu_{k'})}{\kl(\mu_k,\mu_{k'})}\right)^2 + 1.
      \end{align*}
    \end{small} % XXX
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  \begin{align*}
    & \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t)\right)  \\ & \leq \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t), A^j(t+1) \in \TopM(t) \cap \{k': U_{k'}^j(t-1) \leq g_k^j(t-1)\}\right) \\
    & \leq   \sum_{t=1}^T \sum_{k' \neq k}\Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right) \\
    & = \sum_{k' \neq k} \underbrace{\sum_{t=1}^T \Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right)}_{:= T_{k'}}
  \end{align*}

@@

  For the sake of clarity, we now explain Figure~\ref{fig:5:StateMachineAlgorithm_MCTopM} in words. At step $t$, if player $j$ is not fixed ($\overline{s^j(t)}$), she can have three behaviors when executing \MCTopM.
  She keeps the same arm and goes to the other state $s^j(t)$ with transition $(1)$,
  or she stays in state $\overline{s^j(t)}$,
  with two cases.
  Either she sampled $A^j(t+1)$ uniformly
  from $\TopM(t) \cap \{ m : g_m^j(t) \leq g_k^j(t) \}$
  with transition $(3)$,
  in case of collision and if $A^j(t+1) \in \TopM(t)$,
  or she sampled $A^j(t+1)$ uniformly
  from $\TopM(t)$ with transition $(2)$,
  if $A^j(t+1) \notin \TopM(t)$.
  In particular, note that if $\overline{C^j(t)}$, transition $(3)$ is executed and not $(2)$.
  %
  % The case $(2)$ happens when there is no collision at time $t-1$ but a collision at time $t$,
  % and conversely case $(3)$ happens when the player was not fixed on her arm at time $t-1$ (\ie, $\overline{s^j(t-1)}$)
  % and experienced a collision at time $t-1$
  Transition $(3)$ is a uniform sampling from $\TopM(t)$ (the ``Musical Chair'' step).

>>>>

Under observation model \modeltrois{} no sensing information is available and the previous algorithms cannot be used, as the sum of sensing information $S_k^j(t)$ and thus the empirical mean $\widehat{\mu}_k^j(t)$ cannot be computed, hence neither the indices $U_k^j(t)$. However, one can still define a notion of \emph{empirical reward} received from arm $k$ by player $j$, by introducing
%
% \vspace*{-5pt}
\begin{equation}
  \widetilde{S_k}^j(t) = \sum_{t=1}^T r^j(t) \indic(A^j(t) = k)
  \ \ \ \text{and letting} \ \ \ \widetilde{\mu_k}^j(t) := \widetilde{S_k}^j(t) \;/\; T_k^j(t).
\end{equation}

Note that $\widetilde{\mu_k}^j(t)$ is no longer meant to be an unbiased estimate of $\mu_k$ as it also takes into account the collision information, that is present in the reward. Based on this empirical reward, one can similarly defined modified indices as
%
\begin{equation}\label{eq:5:indexTilde}
  \widetilde{U_k}^j(t) = \begin{cases}
      \widetilde{\mu_k}^j(t)  + \sqrt{  f(t) / (2T_k^j(t))}
      &\text{for } \UCB, \\
      \sup\left\{ q \in [0, 1]: T_k^j(t)\times \kl(\widetilde{\mu_k}^j(t), q) \leq f(t) \right\}
      &\text{for } \klUCB.
  \end{cases}
\end{equation}

Given any of these two index policies (\UCB{} or \klUCB), the \Selfish{} algorithm is defined by,
%
\begin{equation}
  A^j(t) = \argmax_{ k \in [K]} \ \widetilde{U_k}^j(t-1).\label{algo:5:Selfish}
\end{equation}
The name comes from the fact that each player is targeting, in a ``selfish'' way, the arm that has the highest index, instead of accepting to target only one of the $M$ best.
The reason that this may work precisely comes from the fact that $\widetilde{U_k}^j(t)$ is no longer an upper-confidence on $\mu_k$,
but some hybrid index that simultaneously increases when a transmission occurs and decreases when a collision occurs.

This behavior is easier to be understood for the case of \Selfish-\UCB{} in which, letting $N_k^{j,C}(t) = \sum_{s=1}^t \indic(C^j(t))$ be the number of collisions on arm $k$, one can show that the hybrid \Selfish{} index induces a penalty proportional to the fraction of collision on this arm and the quality of the arm itself:
\begin{equation}
  \widetilde{U_k}^j(t) = U_k^j(t) -
  \underbrace{\left(\frac{N_k^{j,C}(t)}{N_k^j(t)}\right)}_{\text{fraction of collisions}}
  \underbrace{\left(\frac{1}{N_k^{j,C}(t)}\sum_{t=1}^{T}Y_{A^j(t),t} \indic(C^j(t)) \indic(A^j(t) = k)\right)}_{\text{estimate of } \mu_k }.
\end{equation}

@@

\paragraph{Index policies.}
%
The approaches we now describe for multi-player bandits can be used in combination with any index policy, but we restrict our presentation to UCB algorithms, for which strong theoretical guarantees can be obtained. In particular, we focus on two types of indices:
\UCB{} indices \citep{Auer02}
and \klUCB{} indices \citep{KLUCBJournal}, that can be defined for each player $j$ in the following way.
%
Letting $S_k^j(t) := \sum_{s=1}^t Y_{k,s} \indic(A^j(t) = k)$ the current sum of rewards obtained by player $j$ for arm $k$,
then $\widehat{\mu}_k^j(t) = S_k^j(t)/T_k^j(t)$ (if $T_k^j(t)\neq 0$) is the empirical mean of arm $k$ for player $j$, and thus one can define the index
\begin{equation}\label{eq:5:indexFor_UCB_klUCB}
  U_k^j(t) := \begin{cases}
      \widehat{\mu}_k^j(t)  + \sqrt{  f(t) / (2T_k^j(t))}
      &\text{for } \UCB, \\
      \sup\left\{ q \in [0, 1]: T_k^j(t)\times \kl(\widehat{\mu}_k^j(t), q) \leq f(t) \right\}
      &\text{for } \klUCB,
  \end{cases}
\end{equation}
where $f(t)$ is some \emph{exploration function}. $f(t)$ is usually taken to be $\log(t)$ in practice, and slightly larger in theory, which ensures that  $\Pr(U_k^j(t) \geq \mu_k) \gtrsim 1 - 1/t$ (see \cite{KLUCBJournal}).
A classical (single-player) UCB algorithm aims at the arm with largest index. However, if each of the $M$ players selects the arm with largest UCB, all the players will end up colliding most of the time on the best arm.
To circumvent this problem, several coordination mechanisms have emerged, that rely on \emph{ordering} the indices and targeting \emph{one of} the $M$-best indices.

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(1) \sim \cU([K])$ and $C^j(1)=\mathrm{False}$ \\
              \For{$t = 0, \dots, T - 1$}{
                  %
                  \eIf{$A^j(t) \notin \TopM(t)$}{
                    \eIf(\tcp*[f]{collision}){$C^j(t)$}{
                      $A^j(t+1) \sim \cU \left(\TopM(t)\right)$
                      \tcp*[f]{randomly switch}
                      }(\tcp*[f]{randomly switch on an arm that had smaller UCB}){
                        $A^j(t+1) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      }
                    }{
                      $A^j(t+1) = A^j(t)$
                      \tcp*[f]{stays on the same arm}
                    }
                  Play arm $A^j(t+1)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \RandTopM{} decentralized learning policy]{The \RandTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:RandTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

% \vspace*{-5pt}  % XXX remove if problem
% \begin{small}  % XXX remove if problem
  \begin{figure}[h!]
      \begin{framed}  % XXX remove if problem
      % \begin{small}  % XXX remove if problem
      \centering
      % Documentation at http://mirror.ctan.org/tex-archive/macros/latex/contrib/algorithm2e/doc/algorithm2e.pdf if needed
      % Or https://en.wikibooks.org/wiki/LaTeX/Algorithms#Typesetting_using_the_algorithm2e_package
      % \removelatexerror% Nullify \@latex@error % Cf. http://tex.stackexchange.com/a/82272/
      \begin{algorithm}[H]
          % XXX Options
          % \LinesNumbered  % XXX Option to number the line
          % \RestyleAlgo{boxed}
          % XXX Input, data and output
          % \KwIn{$K$ and policy $P^j$ for arms set $[K]$\;}
          % \KwData{Data}
          % \KwResult{Result}
          % XXX Algorithm
              Let $A^j(1) \sim \cU([K])$ and $C^j(1)=\mathrm{False}$ and $s^j(1)=\mathrm{False}$ \\
              \For{$t = 0, \dots, T-1$}{
                   \uIf(\tcp*[f]{transition $(3)$ or $(5)$}){
                      $A^j(t) \notin \TopM(t)$}
                    {
                      $A^j(t+1) \sim \cU \left(\TopM(t) \cap \left\{k : U_k^j(t-1) \leq U^j_{A^j(t)}(t-1)\right\}\right)$
                      \tcp*[f]{not empty} \\
                      % \tcp*[f]{randomly switch on an arm that had smaller UCB}
                      $s^j(t+1) = \mathrm{False}$
                      \tcp*[f]{aim at an arm with a smaller UCB at $t-1$}
                    }
                    \uElseIf(\tcp*[f]{collision and not fixed}){
                        $C^j(t)$ \emph{and} $\overline{s^j(t)}$}
                      {
                        $A^j(t+1) \sim \cU \left(\TopM(t)\right)$
                        \tcp*[f]{transition $(2)$} \\
                        $s^j(t+1) = \mathrm{False}$
                    }
                    \Else(\tcp*[f]{transition $(1)$ or $(4)$}){
                      $A^j(t+1) = A^j(t)$ \tcp*[f]{stay on the previous arm} \\
                      $s^j(t+1) = \mathrm{True}$ \tcp*[f]{become or stay fixed on a ``chair''}
                    }
                  Play arm $A^j(t+1)$, get new observations (sensing and collision), \\
                  Compute the indices $U^j_k(t+1)$ and set $\TopM(t+1)$ for next step.
              }
              \caption[The \MCTopM{} decentralized learning policy]{The \MCTopM{} decentralized learning policy (for an index policy $U^j$).}
          \label{algo:5:MCTopM}
      \end{algorithm}
      % \end{small}  % XXX remove if problem
      \end{framed}  % XXX remove if problem
  \end{figure}
% \end{small}  % XXX remove if problem
% \vspace*{-5pt}  % XXX remove if problem

@@

\begin{smallproof}
  %
  %     Recall $U_k^j(t) \in \mathbb{R}$ denote the index of arm $k$ for user $j$ at time $t$.
  %     As only user $j$ is considered here, the superscript $j$ is dropped.
  %
  Fix $k\in\Mworst$ and a player $j \in [M]$.
  The key observation is that for \MCTopM, \RandTopM{} as well as the \rhoRand{} algorithm, it holds that
  \begin{equation}\left(A^j(t) = k\right) = \left(A^j(t) = k , \exists m \in \Mbest : U_m^j(t) < U_k^j(t) \right).\label{eq:5:KeyInclusion}\end{equation}
  Indeed, for the three algorithms, an arm selected at time $t+1$ belongs to the set $\TopM(t)$ of arms with $M$ largest indices.
  If the sub-optimal arm $k$ is selected at time $t$, it implies that $k \in \TopM(t)$, and, because there are $M$ arms in both \Mbest{} and $\TopM(t)$, one of the arms in \Mbest{} must be excluded from $\TopM(t)$.
  In particular, the index of arm $k$ must be larger than the index of this particular arm $m$.

  Thanks to \eqref{eq:5:KeyInclusion} and if $\Pr_{\bm{\mu}} $ denote here the probability under model $\bm{\mu}$, it is easy to decompose the number of selections of arm $k$ by user $j$ up to round $T$ as
  \begin{align*}
  \E_{\mu}[T_k^j(T)]
  &= \E_{\mu}\left[ \sum_{t=1}^T \mathbbm{1}\left( A^j(t) = k \right) \right]
  = \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k \right).\\
  %&= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in\Mbest,\; U_m(t) < U_k(t) \right) \\
  &= \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\;\; \exists m \in[M]:\; U_{m^*}^j(t) < U_k^j(t) \right).
  %
  \end{align*}

@@

  \begin{align}
    \E_{\mu}[T_k^j(T)] &\leq
    \sum_{t=1}^T\Pr_{\bm{\mu}} \left( \exists m_1 \in [M]: \; U_{m_1^*}(t) < \mu_m^* \right) + \notag \\
    \;\;\;\;
    \sum_{t=1}^T\Pr_{\bm{\mu}} & \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; U_{m_2^*}(t) \leq U_k(t) , \forall {m_3} \in [M]: \;  U_{{m_3}^*}(t) \geq \mu_{m_3}^* \right) \notag \\
    &\leq \sum_{m_1=1}^M\sum_{t=1}^T\Pr_{\bm{\mu}} \left(U_{m_1^*}(t) < \mu_{m_1}^* \right) + \sum_{t=1}^T\Pr_{\bm{\mu}} \left(A^j(t) = k,\;\; \exists m_2 \in [M]:\; \mu_{m_2}^* \leq U_k(t)\right) \notag \\
    %
    & \leq \sum_{m_1=1}^M \sum_{t=1}^T \Pr_{\bm{\mu}} \left( U_{m_1^*}(t) < \mu_{m_1}^* \right)
    + \sum_{t=1}^T \Pr_{\bm{\mu}} \left( A^j(t) = k,\; \mu_{M^*} \leq U_k(t) \right)
    \label{eq:5:sumOfProbaForTkj}
  \end{align}
  where the last inequality (for the first term) comes from the fact that $\mu_{M^*}$ is the smallest of the $\mu_{m^*}$ for $m \in [M]$.

@@

  \begin{lemma}\label{lem:5:Fact1KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
      For any arm $k$, if $U_k^{j}(t)$ is the \klUCB{} index with exploration function $f(t)=\log(t)+3\log\log(t)$,
      \begin{equation}
        \sum_{t=1}^T \Pr_{\bm{\mu}} \left(U_k^{j}(t) < \mu_k\right) \leq 3 + 4e \log\log(T).
      \end{equation}
  \end{leftbar}  % XXX leftbar lemmabar, comment if needed
  \end{lemma}

@@

  \begin{lemma}\label{lem:5:Fact2KLUCB}
  \begin{leftbar}[lemmabar]  % XXX leftbar lemmabar, comment if needed
    For any arms $k$ and $k'$ such that $\mu_{k'} > \mu_{k}$, if $U_k^{j}(t)$ is the kl-UCB index with exploration function $f(t)$,
    \begin{small} % XXX
      \begin{align*}
        &\sum_{t=1}^T\Pr_{\bm{\mu}} \left( A^j(t) = k, \mu_{k'} \leq U_k^{j}(t) \right) & \leq  \frac{f(T)}{\kl(\mu_k,\mu_{k'})}
        + \sqrt{2\pi} \sqrt{\frac{\kl'(\mu_k,\mu_{k'})^2}{\kl(\mu_k,\mu_{k'})^3}}\sqrt{f(T)} + 2\left(\frac{\kl'(\mu_k,\mu_{k'})}{\kl(\mu_k,\mu_{k'})}\right)^2 + 1.
      \end{align*}
    \end{small} % XXX
\end{leftbar}  % XXX leftbar lemmabar, comment if needed
\end{lemma}

@@

  \begin{align*}
    & \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t)\right)  \\ & \leq \sum_{t=1}^T \Pr\left(A^j(t) = k, k \notin \hat{M}^j(t), A^j(t+1) \in \TopM(t) \cap \{k': U_{k'}^j(t-1) \leq U_k^j(t-1)\}\right) \\
    & \leq   \sum_{t=1}^T \sum_{k' \neq k}\Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right) \\
    & = \sum_{k' \neq k} \underbrace{\sum_{t=1}^T \Pr\left(A^j(t) = k,A^j(t+1) = k', U_{k'}^j(t) \geq U_{k}^j(t), U_{k'}^j(t-1) \leq U_{k}^j(t-1)  \right)}_{:= T_{k'}}
  \end{align*}

@@

  For the sake of clarity, we now explain Figure~\ref{fig:5:StateMachineAlgorithm_MCTopM} in words. At step $t$, if player $j$ is not fixed ($\overline{s^j(t)}$), she can have three behaviors when executing \MCTopM.
  She keeps the same arm and goes to the other state $s^j(t)$ with transition $(1)$,
  or she stays in state $\overline{s^j(t)}$,
  with two cases.
  Either she sampled $A^j(t+1)$ uniformly
  from $\TopM(t) \cap \{ m : U_m^j(t) \leq U_k^j(t) \}$
  with transition $(3)$,
  in case of collision and if $A^j(t+1) \in \TopM(t)$,
  or she sampled $A^j(t+1)$ uniformly
  from $\TopM(t)$ with transition $(2)$,
  if $A^j(t+1) \notin \TopM(t)$.
  In particular, note that if $\overline{C^j(t)}$, transition $(3)$ is executed and not $(2)$.
  %
  % The case $(2)$ happens when there is no collision at time $t-1$ but a collision at time $t$,
  % and conversely case $(3)$ happens when the player was not fixed on her arm at time $t-1$ (\ie, $\overline{s^j(t-1)}$)
  % and experienced a collision at time $t-1$
  Transition $(3)$ is a uniform sampling from $\TopM(t)$ (the ``Musical Chair'' step).
